Domain Specific Languages and Code Synthesis

### 2014-03-14 paper.tex
Edits to Section 1

@@

There are many ways to give a computer instructions.
%
%% "might" might sound better than "may"
An electrical engineer might write a MATLAB program,
a database administrator may write an SQL script,
a hardware engineer may write in Verilog,
and an accountant may write a spreadsheet
with embedded formulas.
%
%% This sentence isn't clear, nor does it lead into the next sentence very well.
%% I'd suggest expanding on this point to make it clearer.
Aside from the difference in language, there is an
important difference in {\em form\/} and {\em idiom\/}.
%% Maybe you should emphasise "idiom" as well?
%
All of these examples use languages
customized to the job at hand, and build computational
requests in a form both familiar and productive
for the programmer (though an accountant may
not think of herself as a programmer.)
All these examples are use of domain specific languages.

@@

There are two fundamental types of DSLs
(Figure~\ref{fig:types-of-dsls}).
%
The first, like the SQL example, is when a DSL is a first class language,
with its own compiler or interpreter, and is often used in
its own ecosystem. (Figure \ref{fig:types-of-dsls}(1)) 
All the examples mentioned so far fall
into this category. The primary difference between SQL and
(say) Java is one of scope and focus, though sometimes
DSLs grow to be as large are general purpose languages.
%
The other class of DSLs are languages
embedded inside another hosting language(Figure \ref{fig:types-of-dsls}(2)). 
Such languages
can have the look and feel of being their own languages,
but leverage the host language to provide an existing
eco-structure and initial semantics. 
(Figure \ref{fig:types-of-dsls}, (2))
It is this second
class of DSLs we are interested in, and is the subject of
this paper.

>>>>

\hyphenation{MATLAB} % prevent breaking over lines

@@

There are many ways to give a computer instructions.
%
%% "might" might sound better than "may"
An electrical engineer might write a MATLAB program,
a database administrator may write an SQL script,
a hardware engineer may write in Verilog,
and an accountant may write a spreadsheet
with embedded formulas.
%
%% This sentence isn't clear, nor does it lead into the next sentence very well.
%% I'd suggest expanding on this point to make it clearer.
Aside from the difference in language, there is an
important difference in {\em form\/} and {\em idiom\/}.
%% Maybe you should emphasise "idiom" as well?
%
All of these examples use languages
customized to the job at hand, and build computational
requests in a form both familiar and productive
for the programmer (though an accountant may
not think of herself as a programmer.)
All these examples are uses of domain specific languages.

@@

There are two fundamental types of DSLs
(Figure~\ref{fig:types-of-dsls}).
%
The first, like the SQL example, is when a DSL is a first class language,
with its own compiler or interpreter, and is often used in
its own ecosystem. (Figure \ref{fig:types-of-dsls}(1)) 
All the examples mentioned so far fall
into this category. The primary difference between SQL and,
for instance, Java is one of scope and focus, though sometimes
DSLs grow to be as large as general purpose languages.
%
The other class of DSLs are languages
embedded in a host language(Figure \ref{fig:types-of-dsls}(2)). 
Such languages
can have the look and feel of being their own languages,
but leverage the host language's existing
ecosystem and initial semantics. 
(Figure \ref{fig:types-of-dsls}, (2))
It is this second
class of DSLs we are interested in, and is the subject of
this paper.
